
%=== File containing Global Configuration of the report ===%
%                                                          %
% Copyright (C) ISI - All Rights Reserved                  %
% Proprietary                                              %
% Written by Med Hossam <med.hossam@gmail.com>, April 2016 %
%                                                          %
% @author: HEDHILI Med Houssemeddine                       %
% @linkedin: http://tn.linkedin.com/in/medhossam           %
%==========================================================%

%=========== You MUST type your information here ==========%
% global_config.tex file is designed to configure your     %
% cover pages (main, back and black covers)                %
%==========================================================%

%============= Config new columns type ==============%
\newcolumntype{L}{>{\raggedright\arraybackslash}}
\newcolumntype{R}{>{\raggedleft\arraybackslash}}
\newcolumntype{C}{>{\centering\arraybackslash}}
%==================================================%

%========= Config the cover section ==========%

\title{Conception et Développement d'une plateforme d'apprentissage automatique}

\author{Sami GHORBEL}
%%% if necessary
% Set isBinomal to true and type second author name
%\setboolean{isBinomal}{true}
%\secondAuthor{Prénom NOM}

\diplomaName{Diplôme National d'Ingénieur en Sciences Appliquées et Technologiques}
\speciality{Génie Logiciel et Systèmes d'Information}
%\speciality{Génie des Télécommunications et Réseaux}
%\speciality{Génie Informatique des Systèmes Industriels}

%% Encadrant professionnel
\proFramerName{Monsieur
Aymen BEL ARBI}
\proFramerSpeciality{Ingénieur R\&D}

%% Encadrant académique
\academicFramerName{Madame Olfa MOURALI}
\academicFramerSpeciality{Maître Assistante}

%% Entreprise d'accueil
\companyName{SOFRECOM}

%% Année universitaire
\collegeYear{2016 - 2017}

%%%%%% Signatures section %%%%%%

% You can simply remove theses sentences by typing an empty string
% \proSignSentence{}

\proSignSentence{J'autorise l'étudiant à faire le dépôt de son rapport de stage en vue d'une soutenance.}

\academicSignSentence{J'autorise l'étudiant à faire le dépôt de son rapport de stage en vue d'une soutenance.}

%%% AR
\arabicAbstract{نظرا للمشاكل التي تواجهها سوفريكوم في أداء مهام التنبؤات التي من شأنها أن تساعد على اتخاذ قرار بشأن استقالة موظفيها في المستقبل، وقد بدأ مشروع لتحسين معالجة هذه المهام. والهدف من ذلك هو تنفيذ تطبيق تكنولوجيا المعلومات الذي يحسن معالجة التنبؤات في الوقت الحقيقي، ويسهل ويحسن الإدارة. وقد تحقق هذا المشروع ضمن شركة سوفركوم من خلال تنفيذ الدراسة وتحليلها، وتصميم التطبيق ونمذجة عملياته، وأخيرا تطوير واختبارات التطبيق.}

\arabicAbstractKeywords{التنبؤ، التعلم الآلي، MVC، H2O.AI، API.}

%% To use latin characters inside the arabic text
% just put them inside the command \textLR{}
%%%%

%%% FR
\frenchAbstract{Face aux problèmes rencontrés par Sofrecom dans l'exécution des tâches des prédictions qui vont l'aider à prendre la décision sur la démissions de ses employés dans le futur, un projet d’optimisation du traitement de ces tâches a été engagé. L’objectif est de mettre en place une application informatique qui permet d’améliorer le traitement des prédictions en temps réel, de faciliter et d’améliorer leur gestion. Ce projet a été réalisé au sein de la société Sofrecom en procédant à l’étude et à l’analyse de l’existant, la conception de l’application et la modélisation de ses processus, et enfin le développement et les tests de l’application.}

\frenchAbstractKeywords{Prédiction, Apprentissage Automatique, MVC, H2O.AI, API.}

%%% EN
\englishAbstract{In front of problems met by the company Sofrecom in the execution of the tasks of the predictions that will help it to take a decision on the resignation of its employees in the future, a project to optimize the treatment of these tasks has been initiated. The objective is to set up an IT application that will improve the processing of real-time predictions, and facilitate and improve their management. This project was realized out within the company Sofrecom by proceeding to the study and to the analysis of the existing, the conception of the application and the modelling of its processes, and finally the development and the tests of the application.}

\englishAbstractKeywords{Prediction, Machine learning, MVC, H2O.AI, API.}

%% if you want to get rid of the company address just set the boolean variable to false
% PS : it's optional
\setboolean{wantToTypeCompanyAddress}{true}

\companyEmail{contact@company.com}
\companyTel{71 111 111}
\companyFax{71 222 222}
\companyAddressAR{نهج بحيرة ملاران - ضفاف البحيرة - تونس}
\companyAddressFR{Rue du Lac Malaren, Les Berges du Lac 1053 Tunis}